---
title: "Assessment 1 - NAME"
output: 
  html_document: 
    theme: yeti
---
#  {.tabset}

## R exercises - In class

### Exercise 1
Code description
```{r R-Ex1, echo=TRUE, eval=TRUE}
print("Code")
```

### Exercise 2
Code description
```{r R-Ex2, echo=TRUE, eval=TRUE}
print("Code")
```

### Exercise 3
Code description
```{r R-Ex3, echo=TRUE, eval=TRUE}
print("Code")
```

### Exercise 4
Code description
```{r R-Ex4, echo=TRUE, eval=TRUE}
print("Code")
```

### Exercise 5
Code description
```{r R-Ex5, echo=TRUE, eval=TRUE}
print("Code")
```

### Exercise 6
Code description
```{r R-Ex6, echo=TRUE, eval=TRUE}
print("Code")
```

### Exercise 7
Code description
```{r R-Ex7, echo=TRUE, eval=TRUE}
print("Code")
```

### Exercise 8
Code description
```{r R-Ex8, echo=TRUE, eval=TRUE}
print("Code")
```

## Bash exercises - In class

### Exercise 1
Code description
```{bash, Bash-ex1, echo=TRUE, eval=FALSE}
echo code
```

### Exercise 2
Code description
```{bash, Bash-ex2, echo=TRUE, eval=FALSE}
echo code
```

### Exercise 3
Code description
```{bash, Bash-ex3, echo=TRUE, eval=FALSE}
echo code
```

### Exercise 4
Code description
```{bash, Bash-ex4, echo=TRUE, eval=FALSE}
echo code
```

### Exercise 5
Code description
```{bash, Bash-ex5, echo=TRUE, eval=FALSE}
echo code
```

### Exercise 6
Code description
```{bash, Bash-ex6, echo=TRUE, eval=FALSE}
echo code
```

### Exercise 7
Code description
```{bash, Bash-ex7, echo=TRUE, eval=FALSE}
echo code
```

## R exercises - Out of class

### Exercise 1
Code description
```{r R-OOC-Ex1, echo=TRUE, eval=TRUE}
print("Code")
```

### Exercise 2
Code description
```{r R-OOC-Ex2, echo=TRUE, eval=TRUE}
print("Code")
```

### Exercise 3
Code description
```{r R-OOC-Ex3, echo=TRUE, eval=TRUE}
print("Code")
```

### Exercise 4
Code description
```{r R-OOC-Ex4, echo=TRUE, eval=TRUE}
print("Code")
```

## Bash exercises - Out of class

### Exercise 1
Code description
```{bash, Bash-OOC-ex1, echo=TRUE, eval=FALSE}
echo code
```

### Exercise 2
Code description
```{bash, Bash-OOC-ex2, echo=TRUE, eval=FALSE}
echo code
```

### Exercise 3
Code description
```{bash, Bash-OOC-ex3, echo=TRUE, eval=FALSE}
echo code
```

## R Markdown exercise

### Exercise 1
Code description

### Exercise 2
Code description